Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2014-09-22 Article.tex
update table and figure 8

\newcolumntype{h}{>{\centering}p{40mm}<{}}

\begin{center}
\begin{figure}
\scriptsize
\begin{tabular}{|h|h|}
  \hline
  \textbf{Notations} & \textbf{Meaning} \tabularnewline
  \hline 
  $ \mathcal{A}=\{a_{1},...,a_{N}\} $ & Set of agents \tabularnewline
  $ P_{i}(t) \in \mathbb{R}\ \ (P_{S}(t)) $ & Instantaneous available production of agent i (coalition S) at time t \tabularnewline
  $ \mathcal{T}_{i} = \{P_{i}(t_{0}),...,P_{i}(t_{K})\} $ & Time serie of agent i available production values \tabularnewline
  $ \mathcal{P}_{i}\ \ (\mathcal{P}_{S}) $ & Probability distribution of agent i (coalition S) available production values \tabularnewline
  $ \phi \in [0,1] $ & Reliability threshold (fixed by the grid operator) \tabularnewline
  $ P^{MIN} \in \mathbb{R}^+ $ & Min value threshold (fixed by the grid operator) \tabularnewline
  $ P_{S}^{CRCT} \in \mathbb{R}^+ $ & Contract value of coalition S \tabularnewline
  $ P_{\phi}(S) \in \mathbb{R}^+ $ & Max contract value under $ \phi $ constraint \tabularnewline
  $ \mathcal{U}_{\phi,\ P^{MIN}}(S) $ & Utility function \tabularnewline
  $ \tau_{i}(S) \in \mathbb{R}$ & Descision rule for mapping overlaping into disjoint coalitions \tabularnewline
  $ \epsilon \in [0,1] $ & Pruning threshold for the correlation graph \tabularnewline
  $ N_{COAL} \in \mathbb{Z}^+ $ & Number of desired coalition (entry of the algorithms) \tabularnewline
  $ CS = \{S_{1},...,S_{N_{COAL}}\} $ & Coalition structure \tabularnewline
  \hline
\end{tabular}
\caption{Model main notations}
\label{Fig89}
\end{figure}
\end{center}

>>>>

\begin{table}[!t]
\label{Fig89}
\centering
\scriptsize
\begin{tabular}{l|p{4.5cm}}
  \hline
  \textbf{Symbols} &  \\
  \hline 
  $ \mathcal{A}=\{a_{1},...,a_{N}\} $ & Set of agents \\
  $ P_{i}(t) \in \mathbb{R}\ \ (P_{S}(t)) $ & Instantaneous production of agent $i$ in coalition $S$ at time $t$ \\
  $ \mathcal{T}_{i} = \{P_{i}(t_{0}),...,P_{i}(t_{K})\} $ & Time series of agent i available production values \\
  $ \mathcal{P}_{i}\ \ (\mathcal{P}_{S}) $ & Probability distribution of the production of the agent i in coalition S\\
  $ \phi \in [0,1] $ & Reliability threshold \\
  $ P^{MIN} \in \mathbb{R}^+ $ & Min value threshold \\
  $ P_{S}^{CRCT} \in \mathbb{R}^+ $ & Contract value of coalition S \\
  $ P_{\phi}(S) \in \mathbb{R}^+ $ & Max contract value under $ \phi $ constraint \\
  $ \mathcal{U}_{\phi,\ P^{MIN}}(S) $ & Utility function \\
  $ \tau_{i}(S) \in \mathbb{R}$ & Decision rule for mapping overlapping into disjoint coalitions \\
  $ \epsilon \in [0,1] $ & Pruning threshold for the correlation graph \\
  $ N_{COAL} \in \mathbb{Z}^+ $ & Number of desired coalition \\
  $ CS = \{S_{1},...,S_{N_{COAL}}\} $ & Coalition structure \\
  \hline
\end{tabular}
\caption{Notations}
\end{table}
